Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
tightening

\begin{abstract}
As the software development community continues to make it easier for everyone
to contribute, the number of commits and pull requests keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that social factors cause a noticeable increase
in predictive power (12\%), core team members are more likely to pass the build
tests (10\%), and users with 1000 or more follower are more likely to
pass the build tests (10\%).
\end{abstract}

@@

To investigate our research questions, we built a data set based on the 
attributes that consisted of both technical and social factors.

\paragraph{Technical Factors} We collected these factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy the commit's
complexity, such as the size of the changes being performed.  
The technical
factors used are listed below:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: a count of the lines of code changed by this commit.
\item Files added: a count of the files added by this commit.
\item Files modified: a count of the files modified by this commit.
\item Tests added: a count of the tests added by this commit.
\item Tests deleted: a count of the tests deleted by this commit.
\item Source files: a count of the files in project at the time of the commit.
\item Source loc: a count of the lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

@@

\paragraph{Social Factors} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

We scraped the commit author's
\textit{username} from each commit page, and then
collected user's public profile information. 
%(\textit{https://github.com/\textbf{UserName}}). 
%
The scraper then extracted the following items from the user's
profile.

@@

These social factors are all factors that are tied to a GitHub user's profile.
These factors are likely to increase as developers spend more time on the site
and gain more open source experience.  Thus, we use them as a proxy for
experience.

We also added one item from the MSR Challenge data set to the social factors that indicates if the commit's developer is a core member 
of that project.

\paragraph{Comparing two data sets} We compiled all the gather data into 
two data sets: one with only the technical
factors and the build status, and another with both the technical and social
factors and the build status. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

The data set used in this study~\cite{msr17challenge} is very diverse,
and consists of commits that date as far back as 2011. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014,2015,2016).  This is with the intuition that the social attributes are more likely to have similar values in the most recent years than if we were to consider the whole time span of the projects in the data set.

Since we are interested in the success of the job status of each contribution, we 
converted the Travis build statuses to just two possible values,
successful (passed in the original provided data set) and unsuccessful 
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
At this point 74.43\% of the builds were successful, the rest were not
successful.  This means that a classifier which guesses successful every time
would produce a classification rate of 74.43\% if ran on the full data
set.

>>>>

\begin{abstract}
As the software development community continues to make it easier for everyone
to contribute, the number of commits and pull requests keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that while social factors cause a noticeable increase
in predictive power (12\%), further investigation into these factors are
required.\todo{drop the post-comma clause and instead summarize the specific
  effects we investigated (contributor, followers, etc).}
\end{abstract}

@@

We built a data set of
attributes consisting of both technical and social factors:

\vspace{1ex}
\noindent\textbf{Technical Factors} We collected technical factors from the 
MSR Challenge data set~\cite{msr17challenge}.
We extracted only the attributes in the data set that proxy a commit's
complexity, such as commit size. 
The technical factors used are:
\begin{itemize}
%\item tr\_original\_commit
%\item gh\_build\_started\_at 
\item Source churn: a count of the lines of code changed by this commit.
\item Files added: a count of the files added by this commit.
\item Files modified: a count of the files modified by this commit.
\item Tests added: a count of the tests added by this commit.
\item Tests deleted: a count of the tests deleted by this commit.
\item Source files: a count of the files in project at the time of the commit.
\item Source loc: a count of the lines of source code in the project at
	the time of the commit.
\item Travis status: status of the Travis build integration.
\end{itemize}

@@

\vspace{1ex}
\noindent\textbf{Social Factors} To collect the social data, we created a web scraper to extract the social data
from developer's profiles.
We used the commit hash and the project name in the original data
set provided by the MSR Challenge~\cite{msr17challenge} to locate the web page
of the commit, leveraging \textit{github.com}'s URL standard for projects and
commit hashes.
%  using the syntax
% below. 
% \newline \newline
% \textit{https://github.com/\textbf{NameOfProject}/commit/\textbf{CommitHash}}
% \newline \newline

We scraped the commit author's
\textit{username} from each commit page, and then
collected the following from the user's public profile information:
%(\textit{https://github.com/\textbf{UserName}}). 
%

@@

These social factors are all factors that are tied to a GitHub user's profile
and that are generally correlated with user time and engagement with the site.
Thus, we use them as a proxy for
experience.
We also added one item from the MSR Challenge data set, indiating
whether the commit's developer is a core member  
of the associated project.

\vspace{1ex}
\noindent\textbf{Comparing two data sets.} We compiled the gathered data into 
two data sets: one with only the technical
factors and the build status, and another with both technical and social
factors and the build status. We performed this split to analyze how well technical factors alone,
and then both technical and social
factors predict build integration status.

Our data set~\cite{msr17challenge} is very diverse, consisting
of commits that date as far back as 2011. The social data we 
gather is recent, gathered in January 2017. In an effort to mitigate the threat of
using future result to predict previous events,
we removed the commits in the data set that were not performed within the last
three years of the data set's release (2014--2016).  Our intuition is
that the social attributes are less likely to have substantively changed over a
recent time span.

Since we are interested in the success of the job status of each contribution, we 
converted all Travis build statuses to two possible values:
\emph{successful} (passed in the original provided data set) and \emph{unsuccessful}
(errored, failed, canceled
and started in the original data set). We also condensed down all passing and
failing builds in a commit to a single pass or fail for each build status.  If
the commit contained both passing and failing build statuses, this means it is a failed build and we qualify it as such.
At this point 74.43\% of the builds were successful, the rest were not
successful.  This means that a classifier which guesses successful every time
would produce a classification rate of 74.43\% if ran on the full data
set.
